Contextual Combinatorial Cascading Bandits

### 2015-11-26 contextual combinatorial cascading bandits.tex
update 'Algorithm' section and main theorem

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Let
$$
\gamma_k' = 1 - \gamma_{k-1}, ~~~1 \leq k \leq K.
$$
By equation (\ref{eq:expectation}), we have 
$$
\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' x_{s,\ba_k^s}).
$$
By ridge regression of data 
$$
\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
$$
where
let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.

\begin{theorem}[Theorem 2 in \cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
$$
\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\norm{\hat{\theta}_t - \theta_*}_{\bV_{t}} \leq \beta_{t}(\delta).
\end{equation}
\end{theorem}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. The UCB of item $a$ at time $t$ is defined as:
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}
By theorem \ref{thm:theta_estimate}, it holds that
\begin{lemma}
\label{lem:estimateU}
For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
$$
0 \leq \bU_t(a) - \theta_*^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_*^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

@@

\begin{theorem}
For any $\delta > 0$, with probability at least $1 - \delta$, we have
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
\end{equation}
\end{theorem}
\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
&\leq 4 \beta_T(\Delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d\log(C_\gamma T)\sqrt{TK})
\end{split}
\end{equation}
\end{proof}

Let
\begin{equation}
C_\gamma = \sum_{k=1}^{K} \gamma_k'^2.
\end{equation}

>>>>

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Here we abuse the notation $\abs{\bA_s}$ to denote the number of elements in the list $\bA_s$. Let
$$
\gamma_k' = 1 - \gamma_{k-1}, ~~~1 \leq k \leq K.
$$
By equation (\ref{eq:expectation}), we have 
$$
\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' x_{s,\ba_k^s}).
$$
By ridge regression of data 
$$
\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get a $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.

Next we build on a good estimate of differences between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
$$
\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_*}_{\bV_{t}} \leq \beta_{t}(\delta).
\end{equation}
\end{theorem}

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of item $a$ by
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When (\ref{eq:estimateTheta}) holds for time $t$, we have
$$
0 \leq \bU_t(a) - \theta_*^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_*^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. Second, it recommends the output $\bA_t$ by the offline oracle with estimated weights $\bU_t$. Third, play $\bA_t$ and observes all feedback of items until first $0$ weight come out; the learning agent observes $\bO_t$ items and $\bw_t(\ba_k^t), 1 \leq k \leq \bO_t$, where $\bw_t(\ba_{\bO_t}^t) = 0, \bw_t(\ba_k^t) = 1, 1 \leq k < \bO_t$ or $\bw_t(\ba_k^t) = 1, 1 \leq k \leq \bO_t = \abs{\bA_t}$. Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote a matrix $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

Here is our main theorem.
\begin{theorem}
Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq 1$ and regularization parameter $\lambda \geq C_\gamma$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT}),
\end{equation}
where
\begin{align*}
f^* &= \min_{1 \leq t \leq T} f_t^*\\
C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
\end{align*}
\end{theorem}
\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d\log(C_\gamma T)\sqrt{TK})
\end{split}
\end{equation}
\end{proof}
